\documentclass[10pt]{article}
\usepackage[margin=4em]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage{fontspec}

\titleformat{\section}{}{\thesection}{0pt}{\vspace{0pt}}[{\titlerule[0.1pt]}]
\setlist[itemize]{leftmargin=2em, topsep=0.5em, itemsep=0pt, label=$+$}
\setlength\parindent{0pt}
\pagestyle{empty}

\begin{document}
\setmainfont{CMU Typewriter Text}
{\bf\huge Wenqi He} \hfill (+1)470-343-5207 | hewenqi96@gmail.com

\section*{Experience}
\textbf{Frontend Engineer, Gllue Software}, Shanghai, China \hfill 2020/11 -- 2022/03
\begin{itemize}
\item Developed Web applications and WeChat mini-programs using React and TypeScript.
\item Designed and developed a view layout system on canvas to support in-app screenshots.
\item Developed features for a UI builder framework,  a JSON form engine, and an image-rendering service.
\item Built a light-weight HTML5 encrypted video streaming player to prevent downloads.
\item Participated in the development and integration of an OAuth 2.0 identity service.
\item Maintained online documentations using TypeDoc, GitLab, Docker and ArgoCD.
\end{itemize}

\vspace{0.5em}
\textbf{Electron Developer, Étude}, Atlanta, GA \hfill 2019/09 -- 2020/03
\begin{itemize}
\item Built features such as table of contents parser, persistent word highlighting, etc.
\end{itemize}

\vspace{0.5em}
\textbf{Web Developer, Georgia Institute of Technology}, Atlanta, GA \hfill 2019/08 -- 2019/12
\begin{itemize}
\item Participated in the development of the MEAN-stack mid-term survey application.
\end{itemize}

\section*{Education}

\textbf{University of Illinois Urbana-Champaign}, Champaign, IL \hfill 2022/08 - Present\\
 M.C.S. in Computer Science \\
 
\textbf{Georgia Institute of Technology}, Atlanta, GA  \hfill 2015/08 -- 2019/12\\
B.S. in Computer Science, Minor in Physics, GPA: 3.97/4.0

\section*{Projects: //github.com/GalMunGral}

\textbf{/telescope:} SOCKS-based Split Proxy [C, Python]   \hfill 2021/04
\begin{itemize}
\item A stable anti-censorship tool for bypassing the Great Firewall, implemented using libuv.
\end{itemize}

\vspace{0.5em}
\textbf{/michelangelo:} Web UI without DOM and CSSOM [TypeScript] \hfill 2022/05
\begin{itemize}
\item A low-level UI framework that implements layout, drawing and event handling on canvas.
\item \underline{//galmungral.github.io/michelangelo}
\end{itemize}

\vspace{0.5em}
\textbf{/replay:}  Front-end Framework and Bundler [TypeScript, JavaScript] \hfill 2020/05
\begin{itemize}
\item React-like famework with in-place diffing, non-blocking rendering, hydration and dependency tracking.
\item Webpack-style bundler with support for dynamic imports, code splitting and ESM-mode dev server.
\end{itemize}

\vspace{0.5em}
\textbf{/react-teletype} Interprocess React Renderer [TypeScript] \hfill 2021/05 
\begin{itemize}
\item React renderer for running apps on the server side or in a shared worker to skip reinitialization.
\end{itemize}

\vspace{0.5em}
\textbf{/hanbun-lang:}  An Esoteric Programming Language [PureScript, TypeScript] \hfill 2021/05
\begin{itemize}
\item An object-oriented stack-based language, with syntax based on Classical Chinese.
\item \underline{//galmungral.github.io/hanbun-lang}
\end{itemize}

\vspace{0.5em}
\textbf{/sketchpad:} A Simple Compiler for a High-Level Language [JavaScript] \hfill 2022/04
\begin{itemize}
\item A language with Lisp syntax, C-like semantics and a compiler for a hypothetical architecture.
\item //galmungral.github.io/sketchpad
\end{itemize}

\vspace{0.5em}
\textbf{/turing-machine}:  Implementation of Turing's Universal Machine [Haskell, Common Lisp] \hfill 2021/12

% Angular, Redux Saga, SWR, ECharts, Linaria, Tailwind, Sass/LESS, Vite, webpack, Rollup, Parcel, GitLab, Docker, ArgoCD, TypeDoc, Confluence, MySQL, MongoDB, ajv, Express, Node.js, Puppeteer

\end{document}

