\documentclass[10pt]{article}
\usepackage[margin=4em]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{blindtext}
\usepackage[T1]{fontenc}

\titleformat{\section}{}{\thesection}{0pt}{\vspace{0pt}}[{\titlerule[0.1pt]}]
\setlist[itemize]{leftmargin=2em, topsep=0.5em, itemsep=0pt, label=$\lambda$}
\setlength\parindent{0pt}
\pagestyle{empty}

\begin{document}

{\bf\huge Wenqi He} \hfill (+1)470-343-5207 | hewenqi96@gmail.com

\section*{Experience}
\textbf{Frontend Software Engineer, Gllue Software, Shanghai} \hfill 2020/11 -- 2021/11
\begin{itemize}
\item Developed main features of multiple web applications and WeChat mini-programs using TypeScript and React.
\item Participated in the maintenance of the company's XML-based user interface builder. 
\item Developed a light-weight form engine and image generation service (Node.js) for mini-programs.
\item Responsible for the front-end integration of the company's identity service, using OAuth 2.0 in certain scenarios.
\item Used Redux Saga, SWR, ECharts, Linaria, Sass/LESS, Tailwind, Vite/webpack/Rollup/Parcel, GitLab, ArgoCD.
\end{itemize}

\vspace{0.5em}
\textbf{Electron Developer, Étude (\texttt{etudereader.com}), Atlanta} \hfill 2019/09 -- 2020/03
\begin{itemize}
\item Built features such as parsing table of contents from raw text, persistent word highlighting, etc.
\end{itemize}

\vspace{0.5em}
\textbf{Part-time Web Developer, Georgia Institute of Technology, Atlanta} \hfill 2019/08 -- 2019/12
\begin{itemize}
\item Participated in the development of the mid-term survey system. Implemented the JSON form feature.
\item Mainly used MongoDB, ajv, TypeScript, Angular, Express, Node.js, Puppeteer.
\end{itemize}

\vspace{0.5em}
\textbf{Front-end Developer Intern, PegasusCRM, Atlanta} \hfill 2018/01 -- 2018/04
\begin{itemize}
\item Mainly used Laravel, jQuery, Sass/LESS, Vue.  Developed a PDF-generation service (Node.js) based on Puppeteer.
\end{itemize}


\section*{Education}
\textbf{B.S. Computer Science, Georgia Institute of Technology, Atlanta} \hfill 2015/08 -- 2019/12
\begin{itemize}
\item  Cumulative GPA: 3.97/4.0, Major GPA: 4.0/4.0. Minor in Physics (\texttt{//galmungral.github.io})
\end{itemize} 

\section*{\texttt{\large github.com/GalMunGral}}

\textbf{\texttt{/telescope}:  (C) A SOCKS-based Split Proxy (Anti-Censorship Tool)}   \hfill 2021/04

\vspace{0.5em}
\textbf{\texttt{/turing-machine}:  (Haskell) Implementation of UTM based on Turing's Paper} \hfill 2021/12

\vspace{0.5em}
\textbf{\texttt{/hanbun-lang:} (TypeScript) An Object-Oriented, Stack-Based Esoteric Programming Language} \hfill 2021/05
\begin{itemize}
\item Demo: \texttt{//galmungral.github.io/hanbun-lang}
\end{itemize}

\vspace{0.5em}
\textbf{\texttt{/replay:} (TypeScript/JavaScript) Front-end Framework and Build Tool} \hfill 2020/05 -- 2020/06
\begin{itemize}
\item Features include a DSL (requires Babel), in-place diffing, non-blocking rendering, hydration and dependency tracking.
\item Provides a ESM-mode dev server and webpack-style bundling with code-splitting and support for dynamic imports.
\end{itemize}

\vspace{0.5em}
\textbf{\texttt{/react-teletype}  (TypeScript) React Renderer Shared across Tabs} \hfill 2021/05 
\begin{itemize}
\item Designed for running apps in shared worker to avoid unnecessary initialization for each new tab.
\end{itemize}

\vspace{0.5em}
\textbf{\texttt{/colosseum}:  (TypeScript) HTML5 Encrypted Streaming Media Player}   \hfill 2021/10
\begin{itemize}
\item Built on the Media Source API, DASH protocol and CryptoJS. Protects video from being downloaded.
\end{itemize}

\vspace{0.5em}
\textbf{\texttt{/layout-sandbox:} (TypeScript) WYSIWYG Drag-and-Drop Layout Builder} \hfill 2021/11

\vspace{0.5em}
\textbf{\texttt{/web-repl:} (JavaScript) Web-based Python REPL and Chat Room}  \hfill 2018/05 


\vspace{2em}
For more, visit GitHub: 
\begin{itemize}
\item \texttt{/preludes}: \textit{Experiments related to formal languages, network protocols and front-end frameworks.}
\item \texttt{/etudes}: \textit{Includes full-stack web, mobile \textup(native\textup), desktop \textup(Electron\textup) applications.}
\item \texttt{/bagatelles}: \textit{Includes webpack plugins for generating atomic CSS, detecting unused files, analyzing coupling, etc.}
\end{itemize}

\end{document}

